\section{Indledning}
Idéen til dette projekt opstod efter en afslappet samtale, hvori en den kommende hovedbruger af vores app gav udtryk for en mangel, hun oplevede. Dette førte til flere, mere detaljerede samtaler om at udvikle en app, der kunne hjælpe med at organisere og holde styr på en køkkenhave. Det førte til følgende problemstilling: \medskip 

\textit{This project is a bachelor project that will take place in spring 2021.
The project will aim to simplify the process of keeping your vegetable garden. This will be done so with an app for Android. It is a cumbersome task to keep track of your vegetable garden. Among other things, here are a few examples:}

\textit{\begin{itemize}
    \item 
    What did I plant where?
    \item
    How much water does this specific plant need?
    \item
    Crop rotation - when and how?
    \item
    When to plant and transplant your plants?
\end{itemize}}

\textit{Currently on the market there are some apps that you can use to track some of these aspects of gardening. The ones we researched primarily lack ease of use as well as certain features, such as crop rotation. The app will be implemented in Kotlin for native Android support and will include the following features:}

\textit{\begin{itemize}
        \item
    The ability to see what you have planted and where
        \item
    An overview of the actions you need to perform and when
        \item
    An overview of crop rotation for your vegetable garden
        \item
    Notifications about your crops and integration with calendar
        \item
    Overview of your plating locations (outdoors, greenhouse, etc.)
        \item
    Lexicon with additional info about plants 
\end{itemize}}

\textit{The following points are open for research but are not required implemented in the application:}
\textit{\begin{itemize}
        \item
    Integration with sensors or other IOT devices
        \item 
    Image analysis for identifying crops
\end{itemize}}
